Accelerating Neural Network Training using Arbitrary Precision Approximating Matrix Multiplication Algorithms

### 2021-04-24 latex/ICPP21/paper.tex
add plot for VGG fast combo time data
update paper and vgg plot

\subsection{Skewed Matrix Multiplication}
When computing square matrix multiplications, we have demonstrated that $\dims{4,4,2}$ and $\dims{4,4,4}$ algorithms have the best performance.
However, algorithms with more skewed aspect ratios will likely perform better for problems with matching skewed matrix multiplication dimensions.
We note that an algorithm for dimensions $\dims{m,n,k}$ can be translated into an algorithm for $\dims{n,m,k}$ and any other reordering of the dimensions \cite{BB15}.
\RZ{transposing row major matrix problem?}
\RZ{Best algorithm for each shape of matrices and its figure}

@@

\section{Application of APA algorithms in VGG-11}
\subsection{VGG-11 Network}
\RZ{description of the model of VGG-11 and VGG-19?}

@@

\subsection{Performance}
\RZ{VGG-11 fully connected layer: BS x 25K x 4K / BS x 4K x 4K / BS x 4K x 1K? with plot}

>>>>

\subsection{Skewed Matrix Multiplication}
When computing square matrix multiplications, we have demonstrated that $\dims{4,4,2}$ and $\dims{4,4,4}$ algorithms have the best performance.
However, algorithms with more skewed aspect ratios will likely perform better for problems with matching skewed matrix multiplication dimensions.
We note that an algorithm for dimensions $\dims{m,n,k}$ can be translated into an algorithm for $\dims{n,m,k}$ and any other reordering of the dimensions \cite{BB15}.
\RZ{transposing row major matrix problem?}
\RZ{Best algorithm for each shape of matrices and its figure}
In order to achieve the best performance on a neural network model VGG-11, which we will apply these APA algorithms on, we decided to measure the performance all 28 algorithms on the shapes of multiplied matrices involved in the fully connected layers of VGG-11.
Each fully connected layers of VGG-11 contains the number of weights of 4096, 4096, and 1000, and the input dimension of the first layer is 25088.
Therefore, there are 9 in total multiplications involved: $\dims{25088, 4096, bs}$.

@@

\section{Application of APA algorithms in VGG-11}

\begin{figure}[hb!]
\centering
\input{plots/VGG_time}
\caption{Total time test on VGG-11 with 6 threads}
\label{fig:vgg}
\end{figure}

\subsection{VGG-11 Network}
\RZ{description of the model of VGG-11 and VGG-19?}

@@

\subsection{Performance}
\RZ{VGG-11 fully connected layer: BS x 25K x 4K / BS x 4K x 4K / BS x 4K x 1K? with plot}
\cref{fig:vgg}
\RZ{Fast Combo: 525, 442, 242}
